### 2016-10-18 Hhh/Hhh.tex
Filling in some more gaps in Hhh chapter

\begin{figure}[h!]
\begin{center}
\subfloat[Signal]{\includegraphics[width=0.5\textwidth]{./Hhh/Plots/CMS-HIG-14-034_Figure-aux_020.pdf}}
\subfloat[\ttbar background]{\includegraphics[width=0.5\textwidth]{./Hhh/Plots/mHvsmttbb_ttbar.pdf}}
\end{center}
\caption{Comparison of the reconstructed heavy Higgs mass using the kinematic fit (blue) and
4-body mass without use of the kinematic fit (black) in signal events with $m_{H} = 300 $GeV (left) and \ttbar background events (right) in 
the 2jet-1tag category of the \mutau channel. The kinematic fit greatly improves the resolution and 
accuracy of the mean of the mass distribution in signal events. \cite{HIG-14-034-additional}}%FIXME plots need to be remade as the bkg one was never released
%on the public twiki so can't have the CMS label on
\label{fig:kinfitvsmjj}
\end{figure}

@@

\section{Systematic uncertainties}
\label{sec:hhh_uncs}

@@

Add combined plot + per channel comparison (?)
Combined of mutau and etau only, or full combination even though not having
worked on fully hadronic?

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.85\textwidth]{Hhh/Plots/Hhh2HDM.pdf}
\caption{Search for \Htohhtobbtautau interpreted in a type II 
2HDM, assuming $m_{H} = m_{A} = m_{H^{+}} = 300$ GeV. The expected (dashed line)
and observed (solid line) exclusion contours at 95\% confidence level are overlaid
on the cross--section of $gg\rightarrow \PHiggs$ production
times the branching ratio of \PHiggs into \hhtobbtautau.
Regions of the \cosba-\tanb plane where the cross--section times branching
ratio is larger than the model-independent upper limit set for $m_{H} = 300 $~GeV 
(see figure FIXME:add plot) are excluded.}
\label{fig:Hhh2HDMOverlaid}
\end{center}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.85\textwidth]{Hhh/Plots/AZh2HDM.pdf}
\caption{Search for \AtoZhtolltautau interpreted in a type II 
2HDM, assuming $m_{H} = m_{A} = m_{H^{+}} = 300$ GeV. The expected (dashed line)
and observed (solid line) exclusion contours at 95\% confidence level are overlaid
on the cross--section of $gg\rightarrow \PHiggsps$ production
times the branching ratio of \PHiggsps into \Zhtolltautau.
Regions of the \cosba-\tanb plane where the cross--section times branching
ratio is larger than the model-independent upper limit set for $m_{A} = 300 $~GeV 
(see figure FIXME:add plot) are excluded.}
\label{fig:AZh2HDMOverlaid}
\end{center}
\end{figure}

@@

The combined interpretation of both analyses in this model is presented in figure \ref{fig:HhhAZhMSSM}.
The exclusion in this scenario is driven by the \AtoZh search, the \Htohh search is not
very sensitive in this model (see figure FIXME add these plots). At 350 GeV the excluded
region drops off, this is due to the turn--on of the
$\PHiggsps \rightarrow \ttbar$ decay which becomes kinematically allowed in this region, 
sharply decreasing the \AtoZh branching ratio.

>>>>

\begin{figure}[h!]
\begin{center}
\subfloat[Signal]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure-aux_020.pdf}}
\subfloat[\ttbar background]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/mHvsmttbb_ttbar.pdf}}
\end{center}
\caption{Comparison of the reconstructed heavy Higgs mass using the kinematic fit (blue) and
4-body mass without use of the kinematic fit (black) in signal events with $m_{H} = 300 $GeV (left) and \ttbar background events (right) in 
the 2jet-1tag category of the \mutau channel. The kinematic fit greatly improves the resolution and 
accuracy of the mean of the mass distribution in signal events. \cite{HIG-14-034-additional}}%FIXME plots need to be remade as the bkg one was never released
%on the public twiki so can't have the CMS label on
\label{fig:kinfitvsmjj}
\end{figure}

@@

\section{Systematic uncertainties}
\label{sec:hhh_uncs}
Two types of systematic uncertainties are considered: normalisation
uncertainties (which affect only the yield of a process), and shape
uncertainties (which affect both the yield and shape of a process). Section \ref{sec:hhh_results_extraction}
describes how these uncertainties are taken into account in the final result.

\subsection{Normalisation uncertainties}
\label{sec:hhh_uncs_norm}

\subsubsection*{Luminosity uncertainty}
The uncertainty on the luminosity measurement amounts to 2.6\% for data collected during
2012 (LUMI POG CITATION?). This uncertainty is applied to all processes in which
the normalisation is estimated using MC samples.

\subsubsection*{Identification, isolation and trigger efficiencies}
A systematic uncertainty due to the uncertainty in efficiency measurements
for the leptons is derived by combining the uncertainties on these measurements
in quadrature. For electrons and muons this leads to a 2\% uncertainty, for hadronic taus a 6\% 
uncertainty is measured on the tau identification efficiency, with an additional uncertainty of 3 \% for
the \Pgt legs of the triggers. This uncertainty is applied to all processes for which
the normalisation is estimated using MC samples.

\subsubsection*{$e\rightarrow\Pgt_{h}$ and $\mu\rightarrow\Pgt_{h}$ fake rates}
The uncertainty on both the $e\rightarrow\Pgt$ fake rate measurement and the
$\mu\rightarrow\Pgt$ fake rate measurement is 30\%. The central value of the $\mu\rightarrow\Pgt$
fake rate is close to 1, which is why it is not applied, but the uncertainty is 
taken into account FIXME check if this is true!

\subsubsection*{B-tag scale factors}
The b-tag scale factors are varied within their uncertainties to determine the effect
on the yields of each process. Both a b-tagging uncertainty and a fake mis-tagging
uncertainty are obtained by considering the percentage by which these backgrounds
change when the scale factors are varied within their uncertainty. The b-tagging
efficiency uncertainty amounts to 1-10\% for most processes in most categories, except for the 2jet-2tag
category where a 70\% uncertainty applies to the W background. Due to the nature
of the estimation method, where other backgrounds are subtracted from the data to 
obtain a W estimate, and the presence of large amounts of \ttbar, a 10\% change in the \ttbar
yield can vary the W yield by such large amounts.
The b mistagging rate uncertainty varies between 1-5\% for all processes in all channels.

\subsubsection*{\MET resolution and response}
Uncertainties on the \MET resolution and response are estimated by varying
the recoil correction parameters within their estimated uncertainties. This 
leads to a 1-10\% uncertainty (depending on category and process)

\subsubsection*{Background normalisation}
\begin{itemize}
\item \Ztautau : the normalisation of the embedded samples attracts a 3.3\% uncertainty, which is derived
from combining the estimated normalisation uncertainty on the embedded samples themselves, and the uncertainty on the \ttbar embedded samples. In addition an uncertainty of 5-6\% for extrapolation from the inclusive selection to the category selection is applied.
\item \Zellell: As this is a very small background after requiring 2 jets, the uncertainty on this estimate is derived from the statistical uncertainty on the yield estimate, which varies between 20-90\%
\item \ttbar: the uncertainty on the \ttbar cross section is 10\%
\item di-boson and single top: the uncertainty on the di-boson and single-top cross section is 15\%
\item \Wjets: As the \Wjets yield is estimated from a high \mT sideband in data, the uncertainty on this yield estimate is primarily due to the statistics available in the control region, the uncertainty range sfrom 10\% in the 2jet-0tag cateogry to 100\% in the 2jet-2tag cateogry
\item QCD: The QCD normalisation uncertainty is obtained by adding the statistical uncertainty on the data-subtracted same-sign region in quadrature with the 10\% uncertainty on the OS/SS ratio. This yields a 20\% uncertainty in the 2jet-0tag category, a 40\% uncertainty in the 2jet-1tag category and a 60-100\% uncertainty in the 2jet-2tag category.
\end{itemize}

\subsection{Shape uncertainties}
\label{sec:hhh_uncerts_shape}

\subsubsection*{Tau energy scale}
The energy of hadronically decaying taus is varied up and down by its 3\% uncertainty. As this directly affects the kinematic fit mass distribution this uncertainty is then applied as a shape uncertainty.

\subsubsection*{Jet energy scale}
The uncertainties on the jet energy corrections are applied by shifting the jet energy up and down by the (\pT and $\eta$ dependent) uncertainty. Again, as this affects the shape of the kinematic fit mass distribution this uncertainty is applied as a shape uncertainty

@@

The $m_{H}^{\text{kinfit}}$ distributions in the \mutau and \etau channel 
are shown in figures \ref{fig:hhh_results_mhkinfit_mutau} and \ref{fig:hhh_results_mhkinfit_etau} 
respectively.

\begin{figure}[h!]
\begin{center}
\subfloat[2jet-0tag]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure_003-a.pdf}}
\subfloat[2jet-1tag]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure_003-b.pdf}}~\\
\subfloat[2jet-2tag]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure_003-c.pdf}}
\end{center}
\caption{Distributions of $m_{H}^{kinfit}$ in the 2jet-0tag, 2jet-1tag and 2jet-2tag categories 
of the \mutau channel. The \Htohhtobbtautau signal for $m_{H} = 300 $GeV at \tanb=2 in the low\tanb MSSM
scenario, multiplied by 10, is also overlaid. FIXME need to remake these plots!}
\label{fig:hhh_results_mhkinfit_mutau}
\end{figure}

\begin{figure}[h!]
\begin{center}
\subfloat[2jet-0tag]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure_004-a.pdf}}
\subfloat[2jet-1tag]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure_004-b.pdf}}~\\
\subfloat[2jet-2tag]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure_004-c.pdf}}
\end{center}
\caption{Distributions of $m_{H}^{kinfit}$ in the 2jet-0tag, 2jet-1tag and 2jet-2tag categories 
of the \etau channel. The \Htohhtobbtautau signal for $m_{H} = 300 $GeV at \tanb=2 in the low\tanb MSSM
scenario, multiplied by 10, is also overlaid. FIXME need to remake these plots!}
\label{fig:hhh_results_mhkinfit_etau}
\end{figure}

None of these distributions show hints of an excess.

The model-independent 95\% CL expected and observed upper limits are shown in 
figure \ref{fig:hhh_results_modelindep}, with figure \ref{fig:hhh_results_modelindep_perchannel}
showing the expected sensitivity per channel. These figures include the contribution from the 
\tautau channel not described in this thesis. Figure \ref{fig:hhh_results_modelindep} shows that
the expected upper limit on the \Htohhtobbtautau process is around 0.3 pb, the observed ranges
from 0.2 pb at low mass to 0.4 pb at high mass. From figure \ref{fig:hhh_results_modelindep}
we can see that the \mutau channel is the most sensitive at masses lower than 320 GeV, with 
the \tautau channel being the most sensitive beyond this mass point. The \etau channel is always
less sensitive than the \mutau channel, but at low mass it is still more sensitive than the \tautau 
channel.

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.7\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure_008-d.pdf}
\caption{Expected and observed 95\% CL upper limits on cross-section times branching ratio
for the \Htohhtobbtautau process. In these limits the three final states of \etau, \mutau and \tautau are combined \cite{CMS-HIG-14-034}.}
\label{fig:hhh_results_modelindep}
\end{center}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.7\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure-aux_033.pdf}
\caption{Expected 95\% CL upper limits on cross-section times branching ratio for the \Htohhtobbtautau process.
The blue line represents the limit for the \tautau channel, the green line for the \mutau channel and the
red line for the \etau channel. The black line shows the limit for all three channels combined. We see that up to around
$m_H = 320$ GeV the \mutau channel is the most sensitive, with the \tautau channel being more sensitive at higher masses. FIXME remake this plot!}
\label{fig:hhh_results_modelindep_perchannel}
\end{center}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.85\textwidth]{Hhh/Plots/Hhh2HDM.pdf}
\caption{Search for \Htohhtobbtautau interpreted in a type II 
2HDM, assuming $m_{H} = m_{A} = m_{H^{+}} = 300$ GeV. The expected (dashed line)
and observed (solid line) exclusion contours at 95\% confidence level are overlaid
on the cross--section of $gg\rightarrow \PHiggs$ production
times the branching ratio of \PHiggs into \hhtobbtautau.
Regions of the \cosba-\tanb plane where the cross--section times branching
ratio is larger than the model-independent upper limit set for $m_{H} = 300 $~GeV 
(see figure \ref{fig:hhh_results_modelindep}) are excluded.}
\label{fig:Hhh2HDMOverlaid}
\end{center}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.85\textwidth]{Hhh/Plots/AZh2HDM.pdf}
\caption{Search for \AtoZhtolltautau interpreted in a type II 
2HDM, assuming $m_{H} = m_{A} = m_{H^{+}} = 300$ GeV. The expected (dashed line)
and observed (solid line) exclusion contours at 95\% confidence level are overlaid
on the cross--section of $gg\rightarrow \PHiggsps$ production
times the branching ratio of \PHiggsps into \Zhtolltautau.
Regions of the \cosba-\tanb plane where the cross--section times branching
ratio is larger than the model-independent upper limit set for $m_{A} = 300 $~GeV 
(see figure \ref{fig:AZhUpperLimits}) are excluded.}
\label{fig:AZh2HDMOverlaid}
\end{center}
\end{figure}

@@

Figure \ref{fig:Hhhlowtanb} shows the cross-section times branching ratio
of the \Htohhtobbtautau process in the MSSM low \tanb scenario. Comparing these values 
to the expected and observed upper limits in figure \ref{fig:hhh_results_modelindep} one
can see that the cross-section times branching ratio in this model is, with exception of a few small 
areas, lower than the upper limits set by this analysis. This analysis on its own is
therefore not sensitive enough to exclude any of the \mA-\tanb region in this model. Note that
at low \tanb ~ \mA and \mH are degenerate, and therefore \mH is not in the studied range of $260-350$ GeV
throughout the entire \mA-\tanb plane shown here.

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.85\textwidth]{Hhh/Plots/Hhhlowtbhigh.pdf}
\caption{Cross-section times branching ratio of the \Htohhtobbtautau process
in the low-\tanb MSSM scenario. No expected and observed exclusion contours
have been overlaid on these figures as the cross-section times branching
ratio is smaller than the upper limits set in figure \ref{fig:hhh_results_modelindep}.}
\label{fig:Hhhlowtanb}
\end{center}
\end{figure}

The \AtoZhtolltautau analysis on the other hand can exclude parts of the \mA-\tanb region
in this model by itself. The expected and observed 95\% CL exclusion contours are overlaid 
on the cross-section times branching ratio for this process in the low \tanb MSSM scenario in
figure \ref{fig:AZhlowtanbOverlaid}. The sharp drop in cross-section times branching ratio, and therefore exclusion,
near \mA $ = 350$ GeV arises from the fact that near this mass the decay $\PHiggsps \rightarrow t\bar{t}$ becomes
kinematically allowed, resulting in a reduction of the \AtoZh branching ratio.

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.85\textwidth]{Hhh/Plots/AZhlowtbhigh.pdf}
\caption{Expected and observed 95 \% CL exclusion limits for the \AtoZhtolltautau analysis
in the low \tanb MSSM scenario, overlaid on the cross-section times branching ratio. Areas where
the cross-section times branching ratio is larger than the upper limits in figure \ref{fig:AZhUpperLimits}
are excluded. The exclusion rapidly drops off at $m_A = 350$ GeV due to the turn-on of the
$ \PHiggsps \rightarrow$ \ttbar process.}
\label{fig:AZhlowtanbOverlaid}
\end{center}
\end{figure}

The combined interpretation of both analyses in this model is presented in figure \ref{fig:HhhAZhMSSM}.
The exclusion in this scenario is driven by the \AtoZh search as the \Htohh search is not
very sensitive in this model. Combining the two analyses we do see that a slightly larger amount
of the \mA-\tanb plane can be excluded than using the \AtoZhtolltautau analysis alone. The features
described for figure \ref{fig:AZhlowtanbOverlaid} are also visible in this figure. A small region of phase
space, at low \mA and low\tanb predicts a light Higgs boson mass that is not compatible with 125 GeV within 3 GeV.
This region is therefore excluded, this is indicated by the red band.
